Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2020-12-16 Latex/journal_v1/pr.tex
update achievable rate for journal

In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type, respectively ($V = V_1 + V_2$).
Assume we have $S$ preallocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
Each Service $v_i\in \{1,2,...,V_i \} $ consists of $U_{v_i}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($i \in \{1,2\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to slice.
Each slice $s_i \in \{1,2,...,S_i \}$, $i \in \{1,2\}$ consists of $K_{s_i}$, $i \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{s,1}$ VNFs for the processing of O-DU,  $M_{s,2}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The achievable data rate for the $i^{th}$ UE request in the $v_{1}^{th}$ application of service type 1 (eMBB) can be written as
\begin{equation}\label{eq1}
\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s1=1}^{S_1}\sum_{k=1}^{K_s} B \log_2({1+ \rho_{u(v_1,i)}^{k,s1}})a_{u(v,i)} b_{v_1, s_1} e^{s_1}_{k,u(v_1,i)},
\end{equation}
where $B$ is the bandwidth of system, $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$b_{v_1, s_1}$ is a binary variable that illustrates whether slice $s_1$ is allocated to service $v_1$ or not. 
$e^{s_1}_{k,u(v_1,i)}$ is the binary variable to show whether the UE $i$ in service $v_1$ using slice $s_1$, is assigned to $k^{th}$ PRB or not.
 and $\rho_{u(v_1,i)}^{k,s1}$ is the SNR of $i^{th}$ UE in $v_{1}^{th}$ service experienced at slice $s_1$ on PRB $k$ which is obtained from
\begin{equation}\label{eq2}
\rho_{u(v_1,i)}^{k,s1} =  \sum_{s1=1}^{S_1}\frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
\end{equation}

@@

Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
Slices can have shared resources. All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}. Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.
There are two processing layers one in the DU and one in the CU of ORAN system, each represented with a VNF. The lower layer (i.e., DU) consists of high-PHY, MAC, and RLC, and the upper layer (i.e., CU) consists of RRC, PDCP and SDAP. Assume we have $M_1$ VNFs in the DU layer and $M_2$ VNFs in the CU layer for processing data.
Each VNF in both layers belongs to one or more slices. So, in the $s^{th}$ slice, there are $M_{s,1}$ VNFs in the DU layer and $M_{s,2}$ VNFs in the CU layer. The VNFs in the DU and CU layers have the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively.
Also, RUs and PRBs can serve more than one slice.
\subsection{The Achievable Rate}
The achievable data rate for the $i^{th}$ UE in the $v^{th}$ service can be written as
\begin{equation}\label{eq1}
\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),
where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from
\begin{equation}\label{eq2}
\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},
where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.
\newline
To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service
\begin{equation}\label{eq3}
\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},
where $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$
and $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise, which is made from signal compression in DU.
Besides, $\boldsymbol{P}_{U_v} = \diag{(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})}$.
\newline
Furthermore, $\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
shows the channel matrix between RU set $\mathcal{R}_s$ to UE set
$\mathcal{U}_v$, besides.
%The channel vector from the RU of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
%\begin{equation}
%\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
%\end{equation}
%where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
%represents the large scale fading matrix.
What's more, it is assumed we have perfect channel state information (CSI).\newline
Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below
\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.
Hence, the interference power of $i^{th}$ UE in $v^{th}$ service can be represented as follow
 I_{u_{(v,i)}} &=
 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},
where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.
Interference signal for each UE is coming from UEs using the same PRB.
If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$. Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline
Let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from the $j^{th}$ RU in $s^{th}$ slice.
From \eqref{eq3}, we have,
\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.
Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}
C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s}}{ \sigma_{q_{r(s,j)}}^2})},
where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .

@@

Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.

@@

d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\

@@

D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.

@@

Where, $F_s = M_{s_1} + M_{s_2}$

>>>>

In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type, respectively ($V = V_1 + V_2$).
Assume we have $S$ preallocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
Each Service $v_j\in \{1,2,...,V_j \} $ consists of $U_{v_j}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to slice.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_{s,1}$ VNFs for the processing of O-DU,  $M_{s,2}$ VNFs for the processing of O-CU-UP and $M_{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
 $\rho_{u(v,i)}^{k,s}$ is the SNR 
\begin{equation}\label{eq2}
\rho_{u(v,i)}^{k,s} =  \frac{p_{u(v,i)}^{k,s}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s} g_{r,u(v,i)}|^2}{BN_0 + I_{u(v,i)}^{k,s}},
\end{equation} 
where $p_{u(v,i)}^{k,s}$ represents the transmission power allocated to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(v,i)}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{r,u(v,i)}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(v,i)}^{k,s} = {\bold{h}_{r,u(v,i)}^{k,s}}({\bold{h}_{r,u(v,i)}^{H \: k,s1}} {\bold{h}_{r,u(v,i)}^{k,s}})^{-1}
\end{equation}
Moreover, $g_{r,u(v,i)} \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}^{k,s1}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{u(v,i)}^{k,s} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u(v,i)}^{k,s}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s1} g_{r,u(v,i)}|^2}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{r=1}^{R}|{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(y,l)}^{k,n} g_{r,u(y,l)}|^2}_{\text{(inter-service interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{s}_{k,u(v,i)}e^{s}_{k,u(v,l)}a_{u(v,i)}a_{u(v,l)} b_{v, s} $
and $\gamma_{2} = e^{s}_{k,u(v,i)}e^{n}_{k,u(y,l)}a_{u(v,i)}a_{u(y,l)} b_{v, s} b_{y,n} $.
Where $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
$e^{s}_{k,u(v,i)}$ is the binary variable to show whether the UE $i$ in service $v$ using slice $s$, is assigned to $k^{th}$ PRB or not.

The achievable data rate for the $i^{th}$ UE request in the $v_{1}^{th}$ application of service type 1 (eMBB) can be written as
\begin{equation}\label{eq1}
\mathcal{R}_{u(v_1,i)}^{e} = \sum_{s_1=1}^{S_1}\sum_{k=1}^{K_s} B \log_2({1+ \rho_{u(v_1,i)}^{k,s_1}})a_{u(v_1,i)} b_{v_1, s_1} e^{s_1}_{k,u(v_1,i)},
\end{equation}
where $B$ is the bandwidth of system.

Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $v_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq1}
\mathcal{R}_{u(v_2,i)}^{u} = \sum_{s_2=1}^{S_2}\sum_{k=1}^{K_s} B (\log_2({1+ \rho_{u(v_2,i)}^{k,s_2}})- \zeta_{u(v_2,i)}^{k,s_2}){\beta}_{u(v_2,i)}^{k,s_2}
\end{equation}
Where ${\beta}_{u(v_2,i)}^{k,s_2}=a_{u(v_2,i)} b_{v_2, s_1} e^{s_2}_{k,u(v_2,i)}$
and $\zeta_{u(v_2,i)}^{k,s_2} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(v_2,i)}^{k,s_2}}{N_{u(v_2,i)}^{k,s_2}}})$

@@

@@

Therefore, the mean arrival data rate of UEs mapped to the $s^{th}$ slice in the CU layer is $\alpha_{s_j} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$, where $a_{v,s}$ is a binary variable which indicates whether the $v^{th}$ service is mapped to the $s^{th}$ slice or not.
Furthermore, the mean arrival data rate of the DU layer is approximately equal to the mean arrival data rate of the first layer $\alpha_{s} =\alpha_{s_j} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$.

@@

d_{s_j} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}},\\

@@

D_{s} = d_{s_j} + d_{s_2} + d_{s_{tr}} \forall s.

@@

Where, $F_s = M_{s_j} + M_{s_2}$
